Recurrent Deep Learning Models and its applications

### 2025-02-16 paper2/main.tex
paper update

>>>>

\newpage
% ######################## Background and Literature Review #########################

% ######################## Project Goals and Objectives ######################################
\subsection{Project Goals and Objectives}

% Project Goals
\subsubsection{Project Goals}
The primary goal of this report is to deeply review on RNN and how it can apply in natural language processing (NLP) tasks. And by comparing the performance of different models. this report aims to provide a detailed comparative analysis of the following RNN-based models:
\begin{itemize}
    \item Vanilla RNN
    \item Long Short-Term Memory (LSTM)
    \item Gated Recurrent Unit (GRU)
\end{itemize}

% Objectives
\subsubsection{Objectives}
\begin{enumerate}
    \item Implement Existing RNN Architectures\\
    Develop models using state-of-the-art deep learning framework, PyTorch, to implement each of the above RNNs model. This includes setting up the network layers, loss functions, and appropriate optimization methods.
    \item Apply the Models on a Benchmark NLP Dataset\\
    Utilize a selected NLP dataset to train and evaluate the performance of each RNN-based model. The dataset will be preprocessed (e.g., tokenization, padding, embedding initialization) to suit sequential data modeling.
    \item Compare Model Performances\\
    Compare different RNN-based models on metrics relevant to the target NLP taskquantitatively and qualitatively. Accuracy, F1, training time scores be used.
    \item Analyze the Impact of Architectural Differences
    Identify and discuss the strengths and limitations of each model architecture through both experimental results and theoretical insights. For example, compare how LSTM and GRU architectures mitigate vanishing gradients and exploding gradients using gating mechanisms relative to a vanilla RNN.
\end{enumerate}

\newpage
% ######################## Project Goals and Objectives ######################################

% ######################## Research Plan / Methodology ######################################
\subsection{Research Plan / Methodology}

% ######################## Research Plan / Methodology ######################################
